---
title: "Weight of Fish"
author: "davy d"
date: "spring 2024"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(leaps)
```

## read in fishy data 
```{r}
fishAll= read.csv ("Fish.csv")
```

```{r}
modelall=lm(Weight~Length1+ Length2+Length3+Height+Width,data=fishAll)
summary.lm(modelall)
```

### Best Models

We find the best models for all three species 

### Best Two regressor model
## Perch 

```{r}
library(leaps)
perch.out <-
    regsubsets(Weight~Length1+ Length2+Length3+Height+Width,
               data = perchFish,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

library(car)
subsets(perch.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
The best two variable predictors are Height and Width.

```{r}
#best model
perchBest2= lm(Weight~Height+Width, data = perchFish)
summary.lm(perchBest2)
```

## Pike

```{r}
pikeFish = filter (fishAll, Species =='Pike')
pikeModel = lm(Weight~Length1+Length2+Length3+Height+Width,data=pikeFish)
summary.lm(pikeModel)
```

### Best Models



### Best Two regressor model
```{r}
library(leaps)
pike.out <-
    regsubsets(Weight~Length1+ Length2+Length3+Height+Width,
               data = pikeFish,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(pike.out)
library(car)
subsets(pike.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
The best two variable predictor for Pike is Length1 and Length3


```{r}
pike2=lm(Weight~Length1+Length2,data=pikeFish)
summary.lm(pike2)
```

## Roach

### Best Models

### Best Two regressor model

## Final Summary Statements
We did the best two variable predictor for Pike, Perch and Roach. xxx had the largest R-squared.