---
title: "Weight of Fish"
author: "davy d"
date: "spring 2024"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(leaps)
```

## read in fishy data 
```{r}
fishAll= read.csv ("Fish.csv")
```

```{r}
modelall=lm(Weight~Length1+ Length2+Length3+Height+Width,data=fishAll)
summary.lm(modelall)
```
In this chart it states adjusted R-squared value for ALLfish is 0.8815.
### Best Models

We find the best models for all three species 

### Best Two regressor model

## Perch 

```{r}
perchFish = filter (fishAll, Species =='Perch')
perch2 = lm(Weight~Length1+Length2+Length3+Height+Width,data=perchFish)
summary.lm(perch2)
```
The best two variable predictors are Height and Width.

```{r}
#best model
perchFish= lm(Weight~Height+Width, data = perchFish)
summary.lm(perch2)
```
In this table it shows the adjusted r-squared value for perch fish is 0.94.
## Pike

```{r}
pikeFish = filter (fishAll, Species =='Pike')
pike2 = lm(Weight~Length1+Length2+Length3+Height+Width,data=pikeFish)
summary.lm(pike2)
```
In this chart the adjusted R-squared value for pike fish is 0.9794.
### Best Models



### Best Two regressor model
```{r}
library(leaps)
pike.out <-
    regsubsets(Weight~Length1+ Length2+Length3+Height+Width,
               data = pikeFish,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(pike.out)
library(car)
subsets(pike.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
The best two variable predictor for Pike is Length1 and Length3


```{r}
pike2=lm(Weight~Length1+Length2,data=pikeFish)
summary.lm(pike2)
```
The adjusted r-squared for roach fish is 0.9558.
## Roach
```{r}
roachFish = filter (fishAll, Species =='Roach')
roach2=lm(Weight~Length1+Length2,data=roachFish)
summary.lm(roach2)
```

This table shows the adjusted r-squared for roach fish is 0.8162.

### Best Models


### Best Two regressor model
```{r}
library(leaps)
roach.out <-
    regsubsets(Weight~Length1+ Length2+Length3+Height+Width,
               data = roachFish,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(roach.out)
library(car)
subsets(roach.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

The best two predictor variables for Roach is Length3 and Width. 

## Final Summary Statements
We did the best two variable predictor for Pike, Perch and Roach. PikeFish had the largest R-squared with a value of 0.9794.